\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{caption}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
}

\title{TU-GUT-SYSY v36: Complete Topological Bootstrap \\ From Primordial Knots to Eternal Anyon Braiders and Advanced Vacuum Engineering Designs}
\author{Simon Soliman \\ Independent Researcher, Rome, Italy \\ tetcollective@proton.me \\ tetcollective.org}
\date{December 2025}

\begin{document}

\maketitle

\begin{abstract}
Version 36 (December 2025) completes the Topological Bootstrap Unified Framework, integrating all prior modules into a coherent picture from cosmic origin to laboratory technology.

Key integrations:
- COSMOBOOT unified: primordial knots as dark matter candidates and source of CMB anomalies.
- KNOTBOOT core: eternal anyon braider from ultraclean turbulence (v35, DOI: 10.5281/zenodo.17991214).
- BOOTTECH expansion with new designs:
  - Design 10: Quantum Vacuum Torque Engine (harvesting rotational momentum from amplified Casimir vacuum stress, based on Vacuum Torque v2, DOI: 10.5281/zenodo.17993196).
  - Design 11: Topological Warp Drive Prototype (fractal shell micro-wormhole thruster using knot-induced negative energy density).

The framework requires no new particles, emerges spacetime and gravity from saturated topological entanglement, and provides falsifiable predictions across cosmology, condensed matter, and quantum vacuum engineering (2026–2040).

All conceptual development, theoretical formulation, design, and writing by Simon Soliman. AI tools used only as assistants – no co-authorship.
\end{abstract}

\section{Introduction}
The Topological Bootstrap Unified Framework (TU-GUT-SYSY) proposes that spacetime, gravity, dark matter, and advanced technological possibilities emerge from saturated topological entanglement in primordial and laboratory knot networks.

v36 represents the completion of this vision, integrating COSMOBOOT, KNOTBOOT, and BOOTTECH into a self-consistent whole.

Related works:
\begin{itemize}
    \item v35 (Eternal Anyon Braider): \href{https://doi.org/10.5281/zenodo.17991214}{DOI: 10.5281/zenodo.17991214}
    \item Vacuum Torque v2: \href{https://doi.org/10.5281/zenodo.17993196}{DOI: 10.5281/zenodo.17993196}
\end{itemize}

\section{COSMOBOOT Unified}
Primordial trefoil knot networks act as stable topological solitons, explaining:
- Baryon asymmetry (v1)
- Dark matter density ($\rho_\text{DM} \approx 0.3$ GeV/cm³)
- CMB anomalies (Cold Spot, Axis of Evil, low-multipole suppression)

\section{KNOTBOOT Core}
Eternal gate-free non-Abelian anyon braider in ultraclean turbulence (v35). Perfect 100\% linking conservation enables natural topological quantum processing.

\section{BOOTTECH Expansion: Advanced Designs}

\subsection{Design 10: Quantum Vacuum Torque Engine}
Based on Vacuum Torque v2 (DOI: 10.5281/zenodo.17993196).  
Anisotropic Casimir configurations with rotational freedom harvest vacuum rotational momentum.  
Topological amplification via knot-induced stress enhances local torque by orders of magnitude.

Predicted lab torque: $10^{-18}$ – $10^{-16}$ N·m.  
Applications: contactless nano-actuators, ultra-sensitive angular sensors.

\subsection{Design 11: Topological Warp Drive Prototype}
Fractal shell micro-wormhole thruster (BOOTTECH series).  
Knot networks generate localized negative energy density sufficient for stable microscopic warp bubbles.

Testable superluminal propagation analogs in optical/condensed matter systems without global causality violation.

\section{Falsifiable Predictions 2026--2040}
\begin{itemize}
    \item Graphene turbulence braiding signatures (2026--2027)
    \item CMB polarization knot patterns (LiteBIRD/CMB-S4)
    \item Vacuum torque amplification in birefringent systems
    \item Warp bubble phase shift in high-precision interferometry
\end{itemize}

\section{Conclusion}
The Topological Bootstrap is now complete: a human-led framework unifying cosmic origin, quantum information, and vacuum engineering through primordial and laboratory topological knots.

\section*{License}
Creative Commons Attribution-NonCommercial 4.0 International (CC BY-NC 4.0)  
\url{https://creativecommons.org/licenses/by-nc/4.0/}

\section*{Declaration on AI Assistance}
All work performed solely by Simon Soliman. Grok 4 (xAI) used exclusively as assistive tool for formatting and discussion – no co-authorship.

\end{document}